### 2014-01-30 inst/examples/Reed.Rmd
Logistic (uniform noise), shows steps in deterministic policy (but not the stochastic).

``` {r }
#f <- RickerAllee
#pars <- c(2, K, 5)
f <- BevHolt
pars <- c(2,4)
K <- (pars[1]-1)/pars[2]

#K <- 100
#pars <- c(1,K)
#f <- function(x,h,p){
#  sapply(x, function(x){
 #   S = max(x - h, 0)
#    p[1] * S * (1 - S/p[2]) + S
#  })
#}

@@

``` {r noise}
#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
pdfn <- function(P, s) dlnorm(P, 0, s)

#z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
#pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
````

@@

@@

>>>>

``` {r }
#f <- RickerAllee
#pars <- c(2, K, 5)

#f <- BevHolt
#pars <- c(2,4)
#K <- (pars[1]-1)/pars[2]

K <- 100
pars <- c(1,K)
f <- function(x,h,p){
  sapply(x, function(x){
    S = max(x - h, 0)
    p[1] * S * (1 - S/p[2]) + S
  })
}

@@

``` {r noise}
#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
#pdfn <- function(P, s) dlnorm(P, 0, s)

z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
````

@@

<!--

@@

-->
